Automatic Parallelization and Transparent Fault Tolerance

### 2017-05-18 pubs/tfp16-draft/paper.tex
works?

             &                & $|$ & \texttt{case} $e$ \texttt{of} $x$ \texttt{\{}  & Case expression, $n \ge 1$\\
             &                &     & \texttt{ } $\mathit{alt}_1$ \texttt{;} \\
             &                &     & \hspace{0.2in} $\dots$ \texttt{;} \\
             &                &     & \texttt{ } $\mathit{alt}_n$ \texttt{\}} \\
%            &                &     & \texttt{\}} \\
\\
Alternatives & $\mathit{alt}$ & ::= & $C\ x_1\dots x_n$ \texttt{->} $e$            & Pattern match, $n \ge 0$ \\
             &                & $|$ & \texttt{\_ ->} $e$                           & Default \\
\\
Heap objects & $\mathit{obj}$ & ::= &\texttt{FUN} $x_1\dots x_n$ \texttt{->} $e$   & Function definition, arity $=n\ge 1$ \\
             &                & $|$ &\texttt{CON} $C\ a_1\dots a_n$                & Saturated constructor, $n \ge 0$ \\
             &                & $|$ &\texttt{THUNK} $e$                            & Thunk---explicit deferred evaluation \\
             &                & $|$ &\texttt{PAP} $f\ a_1\dots a_n$               & Partial application \\
             &                & $|$ & $\mathit{BLACKHOLE}$                         & Evaluation-time black hole \\
\\
Object decl. & $\mathit{odecl}$ & ::=  & $x = \mathit{obj}$                           & Simple binding \\
\\
%%%Constructor defn. & $\mathit{con}$  & ::= & $C\ \mathit{type}_i$ & $i \ge 0$ \\
%%%\\
%%%Datatype defn. &  $\mathit{ddecl}$ & ::= & \texttt{data} [\texttt{unboxed}] & User-defined data type  \\
%%%               &                   &     & $C\ x_i =$                       & $i \ge 0, n > 0$         \\
%%%               &                   &     & $\mathit{con}_1 | \dots |  \mathit{con}_n$ \\
%%%\\
%%%Program      & $\mathit{prog}$ & ::= & $\mathit{(o|d)decl}_1$ \texttt{;}            & Object and data defns, \\
%%%             &                 &     & \texttt{ } $\dots$ \texttt{;}                & distinguished \texttt{main}\\
%%%             &                 &     & $\mathit{(o|d)decl}_n$ & 
Program      & $\mathit{prog}$ & ::= & $\mathit{odecl}_1$ \texttt{;}            & Object and data defns, \\
             &                 &     & \texttt{ } $\dots$ \texttt{;}                & distinguished \texttt{main}\\
             &                 &     & $\mathit{odecl}_n$ & 
%Program      & $\mathit{prog}$& ::= & $f_1\ =\ \mathit{obj}_1$ \texttt{;}          & $n \ge 1$, distinguished \texttt{main}\\
%             &                &     & \texttt{ } $\dots$ \texttt{;} \\
%             &                &     & $f_n\ =\ \mathit{obj}_n$

@@

>>>>

             &                & $|$ & \texttt{case} $e$ \texttt{of} $x$ \texttt{\{}  & Case expression, $n \ge 1$\\
             &                &     & \texttt{ } $\mathit{alt}_1$ \texttt{;} \\
             &                &     & \hspace{0.2in} $\dots$ \texttt{;} \\
             &                &     & \texttt{ } $\mathit{alt}_n$ \texttt{\}} \\
%            &                &     & \texttt{\}} \\
\\
Alternatives & $\mathit{alt}$ & ::= & $C\ x_1\dots x_n$ \texttt{->} $e$            & Pattern match, $n \ge 0$ \\
             &                & $|$ & \texttt{\_ ->} $e$                           & Default \\
\\
Heap objects & $\mathit{obj}$ & ::= &\texttt{FUN} $f\ x_1\dots x_n$ \texttt{->} $e$   & Function definition, arity $=n\ge 1$ \\
             &                & $|$ &\texttt{CON} $C\ a_1\dots a_n$                & Saturated constructor, $n \ge 0$ \\
             &                & $|$ &\texttt{THUNK} $e$                            & Thunk---explicit deferred evaluation \\
             &                & $|$ &\texttt{PAP} $f\ a_1\dots a_n$               & Partial application \\
             &                & $|$ & $\mathit{BLACKHOLE}$                         & Evaluation-time black hole \\
\\
Object decl. & $\mathit{odecl}$ & ::=  & $x = \mathit{obj}$                           & Simple binding \\
\\
%%%Constructor defn. & $\mathit{con}$  & ::= & $C\ \mathit{type}_i$ & $i \ge 0$ \\
%%%\\
%%%Datatype defn. &  $\mathit{ddecl}$ & ::= & \texttt{data} [\texttt{unboxed}] & User-defined data type  \\
%%%               &                   &     & $C\ x_i =$                       & $i \ge 0, n > 0$         \\
%%%               &                   &     & $\mathit{con}_1 | \dots |  \mathit{con}_n$ \\
%%%\\
%%%Program      & $\mathit{prog}$ & ::= & $\mathit{(o|d)decl}_1$ \texttt{;}            & Object and data defns, \\
%%%             &                 &     & \texttt{ } $\dots$ \texttt{;}                & distinguished \texttt{main}\\
%%%             &                 &     & $\mathit{(o|d)decl}_n$ & 
Program      & $\mathit{prog}$ & ::= & $\mathit{odecl}_1$ \texttt{;}            & Object and data defns, \\
             &                 &     & \texttt{ } $\dots$ \texttt{;}                & distinguished \texttt{main}\\
             &                 &     & $\mathit{odecl}_n$ & 
%Program      & $\mathit{prog}$& ::= & $f_1\ =\ \mathit{obj}_1$ \texttt{;}          & $n \ge 1$, distinguished \texttt{main}\\
%             &                &     & \texttt{ } $\dots$ \texttt{;} \\
%             &                &     & $f_n\ =\ \mathit{obj}_n$

@@

Mercury~\cite{bone12:autoparallelism_thesis}.  ``Overall, we have attacked and solved a number of issues that are critical to making automatic parallelism a realistic option for developers.''
